---
title: "Places to live and commute in Switzerland"
author: "M. Kliesch"
date: "1/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load, echo = F}
library(leaflet)

# load data
all <- read.csv(file = "dfComplete.csv", header = T)

```

# General Information
Switzerland is famous for its mountains, lakes, and, among many other things, its well-functioning public transport. However, public transport is only as good as its connection to the remotest places. So if you want to live in the Swiss countryside, how many places are there in Switzerland that are small (in population size) and still well connected to the two major cities Zurich and Bern? How many trains per hour go to Zurich/Bern and how long do they take to get there?


# The Dataset  {.tabset}
The dataset contains information about population size and public transport connections of all populated places in Switzerland that have public transport connections to Zurich or Bern.

##  Column names
The dataset consists of `r nrow(all)` rows and `r ncol(all)` columns with the following column names:

```{r colnames, echo = F}
str(all)
```

## Data description

* `name` - name of the town/village
* `lat` - latitude of the town/village
* `lng` - longitude of the town/village
* `population` - population size
* `toBernPerHMon` - number of connections to Bern per hour on a Monday
* `toZhPerHTue` - number of connections to Zurich per hour on a Tuesday
* ... and so on
* `toBernAnyDay` - number of connections to Zurich per hour on average
* `avDurToZh` - average duration to Zurich
* `avDurToBern` - average duration to Bern


## Example data

```{r head, echo = F}
head(all)
```

# Trains to Zurich

(showing places with population size < 5000)
```{r Zurich, echo = F, message = F, error = F, warning = F}
library(dplyr)

# make a preselection of dataset
zurich <- all %>%
  filter(!is.na(avDurToZh) &
           population < 5000 &
           toZhAnyDay != 0 &
           name != "Zurich") %>%
  mutate(color = ifelse(toZhAnyDay > 3, "green", ifelse(toZhAnyDay > 2,"orange", "red"))) %>%
  mutate(inverseDuration = round((0 - avDurToZh + 130),2),
         avDurToZh = round(avDurToZh,2),
         population = round(population),
         toZhAnyDay = round(toZhAnyDay, 2))


zurich %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(color = zurich$color, lng = zurich$lng, lat = zurich$lat,
             radius = 10, weight = sqrt(zurich$inverseDuration)*5,
             popup = paste(zurich$name, paste(". Size:", zurich$population), paste(". Trains to Zurich per h:",
                                                                            zurich$toZhAnyDay), 
                           paste(". Av. commute time:", zurich$avDurToZh, " min."))) %>%
  addLegend(labels = c("> 3x per hour", "> 2x per hour", "< 2x per hour"), colors = c("green", "orange", "red")) %>%
  addLegend(position = "bottomright", labels = c("Larger Dots = Faster Connection"), colors = "black")

```


# Trains to Bern

(showing places with population size < 5000)
```{r Bern, echo = F, message = F, error = F, warning = F}
library(dplyr)

# make a preselection of dataset
bern <- all %>%
  filter(!is.na(avDurToBern) &
           population < 5000 &
           toBernAnyDay != 0 &
           name != "Bern") %>%
  mutate(color = ifelse(toBernAnyDay > 3, "green", ifelse(toBernAnyDay > 2,"orange", "red"))) %>%
  mutate(inverseDuration = round((0 - avDurToBern + 130),2),
         avDurToBern = round(avDurToBern,2),
         population = round(population),
         toBernAnyDay = round(toBernAnyDay, 2))


bern %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(color = bern$color, lng = bern$lng, lat = bern$lat,
             radius = 10, weight = sqrt(bern$inverseDuration)*5,
             popup = paste(bern$name, paste(". Size:", bern$population), paste(". Trains to bern per h:",
                                                                            bern$toBernAnyDay), 
                           paste(". Av. commute time:", bern$avDurToBern, " min."))) %>%
  addLegend(labels = c("> 3x per hour", "> 2x per hour", "< 2x per hour"), colors = c("green", "orange", "red")) %>%
  addLegend(position = "bottomright", labels = c("Larger Dots = Faster Connection"), colors = "black")
